---
title: "Group Project"
output: html_document
date: "2024-02-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library("tidyverse")
library("janitor")
library("lubridate")
```

# BIS15W24


# Introduction

We will be using data published on Kaggle. The data comes from a spreadsheet with information. The data contains 7 csv files from 2015 to 2022 ranking happiness across different regions and countries in the world. 

In our project we will focus on the 2021 csv file.


# The World Happiness Report
The data is collected by The World Happiness Report which surveys bliss. The report gains worldwide acknowledgment as organizations and governments utilize reports such as this one to influence their policy-making decisions. It is a national average of the responses to the main life evaluation question asked in the Gallup World Poll, which uses the Cantril Ladder.


The reports survey the state of bliss within the world nowadays and appear how the modern science of bliss clarifies variation between the regions of the world. 


The 2021 data that we use in our project utilize a Happiness score which is explained by GDP per capita, Healthy Life Expectancy, Social Support, Freedom to make life choices, etc. 


Our project aims to show the data in a more presentable fashion by including ranges and certain values of countries. 


# Cleaning the data

## Names: 
Janitor work

## Removing variables: 
All variables remained but were not utilized on graphs.

## Joins 
None of the other csv files were joined with 2021 as the column names were not similar and R was not allowing us to. 

## Happiest Country: 

## Highest GDP:


Presentation

## Graphing


















## Sources

https://www.kaggle.com/datasets/mathurinache/world-happiness-report/data?select=2021.csv

